### 2018-07-11 paper/message-passing-design.tex
Makes sphinxes branch compile

\NewScheme{\SPOR}

@@

Say that Alice wants to send a message \(m\) to Bob.
Bob runs the \(\SPOR[\Recv]\) algorithm and Alice runs the \(\SPOR[\Send]\) 
algorithm.
Bob (\ie \(\SPOR[\Recv]\)) creates a reply header using \(\CreateRe\) and gives 
the output to Alice (\ie \(\SPOR[\Send]\)) out-of-band.
At a later point, Alice creates a forward header using \(\CreateFwd\), attaches 
the message \(m\) as payload and sends the package to the first node, \ie 
invokes the \(\SPOR[\Fwd]\) algorithm on the first node (\eg as a remote 
procedure call).
The node will then process the package and in turn forward the package to the 
next node, if itself is not the final destination.

\NewAlgorithm{\Store}{Store}
\NewAlgorithm{\Dec}{Dec}
\NewVariable{\sk}{sk}

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/file_exchange_v2.pdf}
  \caption{\label{fig:file-exchange}%
    A schematic of Alice and Bob sending a message using \(\SPORES\).
    \ding{1} illustrates the layer of the headers that Alice and Bob create.
    In \ding{2}, Alice and Bob exchange the headers out-of-band.
    In \ding{3}, Alice and Bob use two \ac{SPOR} routes, one for messages and 
    one for acknowledgements.
  }
\end{figure}

>>>>

\NewScheme{\SPOR}{SPOR}
\NewScheme{\POR}{POR}

@@

Say that Alice wants to send a message \(m\) to Bob.
Bob runs the \(\SPOR[\Recv]\) algorithm and Alice runs the \(\SPOR[\Send]\) 
algorithm.
Bob (\ie \(\SPOR[\Recv]\)) creates a reply header using \(\CreateHeader\) and 
gives the output to Alice (\ie \(\SPOR[\Send]\)) out-of-band.
At a later point, Alice extends the route using \(\WrapHeader\), attaches the 
message \(m\) as payload (\(\AttachPayload\)) and sends the package to the 
first node, \ie invokes the \(\SPOR[\Fwd]\) algorithm on the first node.
The node will then process the package and in turn forward the package to the 
next node, if itself is not the final destination.

\NewAlgorithm{\Store}{Store}
\NewAlgorithm{\Dec}{Dec}
\NewVariable{\sk}{sk}
\NewAlgorithm{\ExtendRoute}{ExtendRoute}

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/file_exchange_v2.pdf}
  \caption{\label{fig:file-exchange}%
    A schematic of Alice and Bob sending a message using \name.
    \ding{1} illustrates the layer of the headers that Alice and Bob create.
    In \ding{2}, Alice and Bob exchange the headers out-of-band.
    In \ding{3}, Alice and Bob use two \ac{SPOR} routes, one for messages and 
    one for acknowledgements.
  }
\end{figure}
